Models

### 2023-10-17 analysis/models.qmd
who knows

library(tidyverse)
library(ordinal)
library(marginaleffects)
library(modelsummary)
library(parameters)
library(brms)
library(cmdstanr)
library(tidybayes)
library(broom.mixed)
library(ggplot2)
library(ggdist)
library(broom)
library(janitor)
library(gt)
library(here)

>>>>

library(tidyverse)
library(ordinal)
library(marginaleffects)
library(modelsummary)
library(parameters)
library(brms)
library(cmdstanr)
library(tidybayes)
library(broom.mixed)
library(ggdist)
library(broom)
library(janitor)
library(gt)
library(here)
